Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64

### 2018-10-09 PAPER.tex
-Edited paragraph about signal loss from other analysis changes to state that future work will exercise more caution

Finally, we emphasize that the discussion that follows is solely focused on signal loss associated with empirical covariance weighting. As mentioned in Section \ref{sec:SiglossOverview}, there are a number of steps in our analysis pipeline which could lead to loss, including gain calibration, delay filtering, and fringe-rate filtering, which have been investigated at various levels of detail in \citet{parsons_et_al2014} and \citetalias{ali_et_al2015} but are clearly the subject of future work. Here we only focus on the most significant source of loss we have identified and note that other sources of loss may still be present (though at much smaller levels).

>>>>

Finally, we emphasize that the discussion that follows is solely focused on signal loss associated with empirical covariance weighting. As mentioned in Section \ref{sec:SiglossOverview}, there are a number of steps in our analysis pipeline which could lead to loss, including gain calibration, delay filtering, and fringe-rate filtering, which have been investigated at various levels of detail in \citet{parsons_et_al2014} and \citetalias{ali_et_al2015} but are clearly the subject of future work. Here we only focus on the most significant source of loss we have identified and note that Kolopanis et al. (\textit{in prep.}) and other future work will consider additional sources of signal loss and exercise increased caution in reporting results.
